---
title: "p8105_hw6_jy3186"
author: "Jiayi Yang"
date: "2022-11-26"
output: github_document
---
```{r}
library(tidyverse)
library(dplyr)
library(readr)
library(modelr)
```
# Problem 1
```{r setup, include=FALSE}
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 2
Import and tidy the dataset
```{r, message = FALSE}
homicide_df = 
  read_csv(url("https://github.com/washingtonpost/data-homicides/blob/master/homicide-data.csv?raw=true"))
```
Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable of whether homicide is solved. `solve_status` is 1 when remains unsolved, is 0 when it's solved.
```{r, warning= FALSE}
homicide_new =
homicide_df %>% 
  mutate(city_state = str_c(city, state, sep = ", ")) %>% 
  group_by(city_state)

cleaned_df =
  homicide_new %>% 
   mutate(
    solve_status = ifelse(disposition %in% c("Closed without arrest", "Open/No arrest"),1,0),
    victim_age = as.numeric(victim_age)
  ) %>% 
  drop_na() %>% 
  filter( 
          victim_race %in% c("White", "Black"),
         !city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) 

cleaned_df
```
For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors.

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. 
```{r}
fit_glm = 
  cleaned_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    model = map(data, ~glm(solve_status ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
     results = map(model, broom::tidy))%>%
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(OR = exp(estimate),
         CI_lower = exp(estimate -1.96*std.error),
         CI_higher = exp(estimate +1.96*std.error)
         ) %>%
  filter(term == c("victim_sexMale")) %>% 
  select(city_state, term, OR, CI_lower, CI_higher) 
fit_glm
```

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r}
fit_glm %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_higher)) +
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```

## Problem 3
load and tidy data
```{r}
birthweight <- read_csv("birthweight.csv")
birthweight %>% 
  select(bwt, blength, gaweeks, bhead, babysex) %>% 
  drop_na() %>% 
  mutate(
    babysex = case_when(babysex == 1 ~ "Male",
              babysex == 2 ~ "Female") %>% 
      as.factor()
  )
```
regression analysis, made a model
```{r}
model = lm(bwt~gaweeks, data = birthweight)
model
```
show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.
```{r}
resid_plot =
birthweight %>% 
  modelr::add_residuals(model) %>% 
  ggplot(aes(x = gasweeks, y = resid)) + geom_violin()

predict_plot = 
  birthweight %>% 
  modelr::add_predictions(model) %>% 
  ggplot(aes(x = gasweeks, y = resid)) + geom_violin()

```

Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}
model1 = lm(bwt~blength + gaweeks, data = birthweight)
model2 = lm(bwt~bhead*blength*babysex, data = birthweight)
```
Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.
```{r}
cv_df = 
  crossv_mc(birthweight, 100) 
```

```{r}
cv_df =
   cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) %>% 
  mutate(
    mod1 = map(train, ~lm(bwt~gaweeks, data = .x)),
    compare_mod1 = map(train, ~lm(bwt~blength +gaweeks, data = .x)),
    compare_mod2 = map(train, ~lm(bwt~bhead*blength*babysex, data = .x)) 
  ) %>% 
  mutate(
    rmse_mod1 = map2_dbl(mod1, test, ~rmse(model = .x, data = .y)),
    rmse_compare_mod1 = map2_dbl(compare_mod1, test, ~rmse(model = .x, data = .y)),
    rmse_compare_mod2 = map2_dbl(compare_mod2, test, ~rmse(model = .x, data = .y))
  )
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

I will decide to use the third model(compare_mod2) with head circumference, length, sex, and all interactions (including the three-way interaction), because it has the least rmse which is the most reflective in representing the relationship between birthweight and these predictors.

